### 2010-12-11 Text/paper.tex
Minor revisions. Started obtaining asymmetric cap results.

\citet{wang-non-circular} performed numerical simulations by VOF technique to for the non-circular
shaped capillaries as square and triangle shaped capillaries. Some interesting results for bubble
shape depending on the capillary number, Fig. \ref{fig:wang:bubble:shape}. They also included
numerical simulations for the determination of the critical capillary number $\hat{Ca}$, Fig.
\ref{fig:wang:critical:capillary}. 
\begin{figure}
\includegraphics[width=\textwidth]{Figures/wang_bubble_shape.eps}
\caption{The bubble shape across the length for different capillary numbers.
\label{fig:wong:bubble:shape}}
\end{figure}
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/wang_critical_capillary.eps}\hfill
\caption{Bubble radiuses variations over the range of capillary numbers (left) and the relative
velocity for th  \label{fig:wang:critical:capillary}}
\end{figure}

>>>>

\citet{wang-non-circular} performed numerical simulations by VOF technique to for the non-circular
shaped capillaries as square and triangle shaped capillaries. Some interesting results for bubble
shape depending on the capillary number, Fig. \ref{fig:wang:bubble:shape}. They also included
numerical simulations for the determination of the critical capillary number $\hat{Ca}$, Fig.
\ref{fig:wang:critical:capillary}. They also found the relative velocity for the bubble for
different capillary numbers. \ref{fig:wang:critical:capillary}.
\begin{figure}
\includegraphics[width=\textwidth]{Figures/wang_bubble_shape.eps}
\caption{The bubble shape across the length for different capillary numbers.
\label{fig:wang:bubble:shape}}
\end{figure}
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/wang_critical_capillary.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/wang_relative_velocity.eps}
\caption{Bubble radiuses variations over the range of capillary numbers (left) and the relative
velocity depending on the capillary number  \label{fig:wang:critical:capillary}}
\end{figure}
